\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
tweak the recommendations section

\section{Recommendations}
\label{sec:recommendations}
While our design resulted in shorter connection times and greater success, it could still be improved. Thus, we do not recommend our exact design. Instead, we offer some suggestions based on what we learned: \\

@@

We ourselves did not follow the above advice, due to design constraints. But seeing as how our redesigned interface still did not have an ideal success rate, connection time, or configuration time, we think that alternative designs that leverage user input and automation should be considered. We recommend implementing some design changes right away initially to improve on the current design, then consider implementing our advice above. \\

@@

User consent should precede any automated connections to Tor. Alternative methods, such as giving location-specific advice, should be explored as well.

>>>>

\section{Recommendations}
\label{sec:recommendations}
While our design resulted in shorter connection times and greater success,  but it could still be improved. We do not recommend our exact design as the optimal design, although we believe it is an improvement. Instead, we offer some suggestions based on what we learned: \\

@@

We did not try any designs that asked for user inputs, due to design constraints. But we see further room for improvement in success rate, connection time, and configuration time that could be made by leverage user input and automation. Here, we talk about the potential approaches to redesigning the interface:  \\

@@

We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes are still unsatisfactory.
